%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Ph.D. in Behavioral, Psychiatric, and Statistical Genetics, Expected May. 2028} % Degree
    {University of Colorado-Boulder | Institute for Behavior Genetics} % Institution
    {Start from Aug. 2023} % Date(s)
    {} % GPA
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Advisor: Dr. Matthew C. Keller}
        \item {Research Area: Statistical Models and Methods in Genetics}
      \end{cvitems}
    }
      \cventry
    {MS in Applied Mathematics, Expected May. 2027} % Degree
    {University of Colorado-Boulder} % Institution
    {Start from Aug. 2024} % Date(s)
    {} % GPA
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Research Area: Disease Prediction Model with GNN}
      \end{cvitems}
    }

  \cventry
    {M.A. in Psychology} % Degree
    {Wake Forest University} % Institution
    {Aug. 2021 - Aug. 2023} % Date(s)
    {} % GPA
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Advisor: Dr. S. Mason Garrison}
        \item {Research Area: Statistical Methods and Behavior Genetics}
        \item {Master's Thesis: \\
        \textit{Family structures impact statistical power of mitochondrial DNA effect estimation under a novel extended-pedigree model}}
      \end{cvitems}
    }
    
   \cventry
    {B.A. in Sociology} % Degree
    {Shandong University} % Institution
    {Sep. 2016 - June. 2020} % Date(s)
    {} % GPA
    {
      \begin{cvitems} % Description(s) bullet points
        \item {First-Year Major: Software Engineering}
       % \item {Related Courses: Calculus, Linear Algebra, Discrete Mathematics, Social Data Analysis,  Social Research Methods}
        \item {Undergraduate Thesis (Awarded Shandong University 2020 Outstanding Undergraduate Thesis): \\ \textit{The Relationship between Social Media, Pornography, and Self-Objectification-An investigation based on structural equation modeling}}
      \end{cvitems}
    }
    
   \cventry
    {Study Abroad} % Degree
    {The University of Queensland} % Institution
    {Jan. 2019 - July. 2019} % Date(s)
    {} % GPA 
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Courses: Social Psychology, Attitudes and Social Cognition, Learning and Cognition, Psychological Methodology III}
     \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
