%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
%\cvsection{Publication}
\cvsection{Publication and Manuscripts}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvpublications}
%---------------------------------------------------------
  \cvpublication
    {\bullet \textbf{Lyu, X.}, Balbona, J., Chen, T. \& Keller, M. C. (Submitted to \textit{Behavior Genetics}) Multivariate SEM-PGS Model: Using Polygenic Scores to Investigate Cross-Trait Indirect Genetic Effects} 
  \cvpublication
    {\bullet \textbf{Lyu, X.}, Hunter, M. D., Burt, S. A., Good, R., Carroll, S. L., \& Garrison, S. M. (2024) (In press at Behavior Genetics). Detecting mtDNA effects with an Extended Pedigree Model: An Analysis of Statistical Power and Estimation Bias. bioRxiv, 2024–12. \href{https://www.biorxiv.org/content/10.1101/2024.12.19.629449v1.abstract}{link}} 
    
  \cvpublication
    {\bullet Garrison, S. M., Hunter, M. D., \textbf{Lyu, X}., Trattner, J. D., \& Burt, S. A. (2023). BGmisc: An R Package for Extended Behavior Genetics Analysis. \textit{Journal of Open Source Software.}} 
    
  \cvpublication
    {\bullet \textbf{Lyu, X. }(2023). Pedigree Structures Impact Statistical Power of MtDNA Effects Estimation \textit{(Master's Thesis, Wake Forest University).} \href{https://www.proquest.com/docview/2863241367}{Available from ProQuest Dissertations \& Theses A\&I}}
  \cvpublication
    {\bullet \textbf{Lyu, X.} \& Garrison, S.M.(2023). Effects of Genetic Relatedness of Kin Pairs on Univariate ACE Model Performance. \textit{Twin Research and Human Genetics, 26(4-5)}, 257-268. doi:\href{https://www-cambridge-org.colorado.idm.oclc.org/core/journals/twin-research-and-human-genetics/article/effects-of-genetic-relatedness-of-kin-pairs-on-univariate-ace-model-performance/7B99A4A34DF4F54CDF2184676C4744AD}{10.1017/thg.2023.40}} 
    
  \cvpublication
    {\bullet Garrison, S.M., Robertson, H., Trattner, J., McKinzie, L., \textbf{Lyu, X.} \& Rodgers, J.L.. (2022). Using genetically-informed designs to test causal claims without experiments: Discordant-Sibling designs and applications. Revise and resubmit to \textit{AMPSS.}}   
    
%---------------------------------------------------------
\end{cvpublications}
