%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Research Experience} 

\cvsubsection{Methods-Related Work:}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}


%---------------------------------------------------------

    \cventry
    {Master's Thesis Project} % Job title
    {Family structures impact statistical power of mitochondrial DNA effect estimation under a novel extended-pedigree model} % Title
    {Dec. 2022 - Present} % Date(s)
    {Wake Forest University} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Estimated statistical power to detect mtDNA effects from an extended pedigree model under the influence of various population parameters of variance and pedigree structures.}
        \item {Created novel R functions for pedigree simulations varying the number of generations, average offspring per pair, sex ratios of newborns, marriage rate, and presence of twins. }
        \item {Conducted a power analysis for mtDNA effects on human longevity.}
      \end{cvitems}
    }

    \cventry
    {Summer Research Project} % Job title
    {An Analysis on ACE Model Performance as a Function of Same-Sex Twins Genetic Relatedness and Sample Sizes } % Title
    {May. 2022 - Present} % Date(s)
    {Wake Forest University} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Conducted mathematical derivation based on the least squares theory and revealed the positive association between power and genetic relatedness}
        \item {Ran simulations to illustrate the impact of genetic relatedness, sample sizes and A,C,E variance combinations on  power of heritability estimation, overall power and negative estimated parameters.}
        \item {Proposed a workflow to help other researchers evaluate the power and feasibility of their analysis. }
      \end{cvitems}
    }
    
    \cventry
    {First-year Project} % Job title
    {Leveraging the China Family Panel Study: An Estimation of Height Heritability Using Preliminary Kinship Links} % Title
    {Sep. 2021 - Present} % Date(s)
    {Wake Forest University} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed a kinship identification algorithm and identified 116909 kin pairs from CFPS, including 177 twin pairs.}
        \item {Obtained a heritability estimate of .28 by using same-sex twins and opposite-sex DZ twins to fit a univariate ACE model.}
        \item {Ran simulations to corroborate the feasibility to incorporate CFPS as a new resource for behavior genetics.}
      \end{cvitems}
    }
    
    %---------------------------------------------------------
  \cventry
    {Research Assistant at the Research Center for Brain and Mathematics Learning} % Affiliation/role
    {Data Manipulating and Analysis for Several Projects} % Organization/group
    {June. 2020 - Sep. 2020} % Location
    {Beijing Normal University } % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Used Visual FoxPro, R, Python and other means to realize data collection, data extraction, data cleaning, data analysis, data visualization for various projects in the lab. }
        \item {Processed data for more than 10 projects, including the cleaning and analysis of large data with more than 1.7 million data.}
        \item {Developed and maintained standardized SQL and R data cleaning scripts and instructed other lab members in their use.}
      \end{cvitems}
    }
    
        \cventry
    {Research Assistant at Dr. Niklas Steffens' lab} % Job title
    {An Archival Sentiment Analysis of Past-50-Years US Media Narratives around "CEO pay"  } 
    {April. 2019 - Oct. 2019} % Location
    {The University of Queensland} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {A project that posits a significant treatment effect of the Global Financial Crisis (Oct. 2008) on the sentiment fluctuation of “CEO pay.” in US newspapers.}
        \item {Collected 14412 US newspaper pieces around “CEO compensation” from the Factiva database.}
        \item {Utilized an LDA topic model (a text analysis method) to screen the topic-related articles and conducted a regression discontinuity design to analyze sentimental changes in R.}
    %    \item {Prospecting Publication: Steffens, N.K., Lyu, X., Haslam, S.A. \& Quiggin, J. \textit{ Don’t drink the Kool Aid!: Evidence that an increase in positive discourse around CEO pay preceded the 2008 Global Financial Crisis} (In Manuscript).}
      \end{cvitems}
    }
\end{cventries}

\cvsubsection{Content-Related Work:}  

\begin{cventries}
    \cventry
    {Undergraduate Thesis} % Job title
    {A Study on the Relationship between Social Media Use and Self-Objectification} % Title
    {March. 2019 - June. 2020} % Date(s)
    {Shandong University} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {In study 1, revealed that increased social media use predicted increased body shame, and determined that this relationship was mediated by increased social comparison on Facebook and body surveillance, using a sample collected from Amazon Mechanical Turk.}
        \item {In study 2, found that increased use of video pornography on the internet predicted increased self-objectification in both men and women but did not predict increased men’s sexual objectification on women.}
        \item {In the undergraduate thesis, constructed a structural equation model to illustrate the relationship between social media use, pornography exposure and self-objectification, and the gender differences in such process.}
      \end{cvitems}
    }
    
    \cventry
    {Research Assistant} % Job title
    {A Qualitative Study on How Full-time TOEFL, IELTS and GRE Teachers in China Constitute Their Self-perception and Career Identity} % Organization
    {Sep. 2018 - Dec. 2018} % Location
    {Shandong University} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {A study concluded that most teachers failed to gain a self-perception as a “real teacher” due to the short-term and commercial nature of the teacher-student relationship.}
        \item {Participated in in-depth interviews on 18 full-time TOEFL, IELTS and GRE teachers in Jinan and obtained more than 14 hours audio data during the field study in several extra-curricular English tutoring schools.}
      \end{cvitems}
    }
    
    
    \cventry
    {Project Leader} % Job title
    {A Study Investigating The Role of Chinese Migrant Workers' self-perception in Social Identity as Urban Citizens} % Organization
    {June. 2017 - Nov. 2017} % Location
    {Shandong University} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Conducted a survey study of 438 samples to measure Chinese migrant workers' self-perception, social identity as urban citizens and other demographic data.}
        \item {Commenced a public welfare program "M-W Helper" to help migrant workers improve their mental health during the process of urbanization.}
      \end{cvitems}
    }
    
%---------------------------------------------------------

\end{cventries}
