%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Research Talks}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries2}
%---------------------------------------------------------
    \cventryx
    {Talk Given at Symposium at the 54th Behavior Genetics Association Annual Meeting. } % Event
    {Lyu, X., Balbona, J., Kim, Y. \& Keller, C.M., Multivariate SEM-PGS Model: Using Polygenic Scores to Demystify Cross-Trait Genetic Nurture } 
    {June. 2024} % Date(s)
    {London, United Kingdom}
    
    \cventryx
	{Presentation Given at StatGen Meeting at IBG} % Event
    {\textbf{Lyu, X.} \& Noemie Valenza-Troubat. GitHub Tutorial Workshop at IBG} 
    {Nov. 2023} % Date(s)
    {Boulder, US}
    
    \cventryx
	{Guest Lecture in PSYC 3102-Behavior Genetics Course} % Event
    {\textbf{Lyu, X.} Genetic Nurture: New Insights from Family Design in Post-GWAS Era} 
    {Nov. 2023} % Date(s)
    {Boulder, US}
    
    \cventryx
	{Talk Given at the Equinox Conference 2023 } % Event
    {\textbf{Lyu, X.} \& Garrison, S.M. Effects of Genetic Relatedness of Kin Pairs on Univariate ACE Model Performance.} 
    {Sep. 2023} % Date(s)
    {Online}
    
    \cventryx
	{Talk Given at Symposium at the 53rd Behavior Genetics Association Annual Meeting. } % Event
    {Garrison, S.M., \textbf{Lyu, X.}, Hunter, M.D., Rodgers, J.L, Smith, K.R., Coon, H., \& Burt, S.A. Analyzing extended cousin similarity to unravel the mystery of mtDNA and longevity. In Burt, S.A. (Chair), A new extended pedigree model for quantifying the contributions of mitochondrial DNA.} 
    {June. 2023} % Date(s)
    {Murcia, Spain}
    
    \cventryx
	{Talk Given at Symposium at the 53rd Behavior Genetics Association Annual Meeting. } % Event
    {Hunter, M.D., \textbf{Lyu, X.}, Garrison, S.M., Rodgers, J.L, Smith, K.R., Coon, H., \& Burt, S.A. Modeling mtDNA Effects from Extended Pedigrees in the Utah Population Database. In Burt, S.A. (Chair), A new extended pedigree model for quantifying the contributions of mitochondrial DNA.} 
    {June. 2023} % Date(s)
    {Murcia, Spain}
    
    \cventryx
	{Talk Given at Symposium at the 53rd Behavior Genetics Association Annual Meeting. } % Event
    {\textbf{Lyu, X.}, Hunter, M.D., Rodgers, J.L, Smith, K.R., Coon, H., Burt, S.A., \& Garrison, S.M.  Statistical power analysis on mtDNA effects estimation. In Burt, S.A. (Chair), A new extended pedigree model for quantifying the contributions of mitochondrial DNA.} 
    {June. 2023} % Date(s)
    {Murcia, Spain}
    
    \cventryx
	{Talk Given at the Quantitative Methods Section of Behavior Genetics Association 2022 Annual Meeting} % Event
    {\textbf{Lyu, X.} \& Garrison, S.M. Leveraging the China Family Panel Study: An Estimation of Height Heritability Using Preliminary Kinship Links } 
    {June. 2022} % Date(s)
    {Los Angeles, US}
    
    \cventryx
 	{Oral Presentation Earned the 2nd prize of Outstanding Paper at 11th Chinese Psychologist Conference} % Event
    {\textbf{Lyu, X.} Social Media Use Predicts Increased Self-objectification through Social Comparison.}
    {Oct. 2019}
    {Nanjing, China}
\end{cventries2}